ICT and Future Productivity:\\Evidence and Theory of a GPT\thanks{Correspondence: Department of Economics, Boston College, 140 Commonwealth Avenue, Chestnut Hill, MA 02467. Email: brianti@bc.edu (Marco Brianti) and gati@bc.edu (Laura G\'ati).}

### 2018-07-12 Latex/Draft_Summer2018/Summer2018.tex
more editing

In the previous section, we have documented results regarding the relation of current ICT investment and future productivity. Clearly, to rationalize empirical dynamic responses of aggregate macroeconomic variables to ICT shocks, we need a two-sector approach that distinguishes ICT goods from other output. In this section, we present a simple two-sector model that rationalizes our structural VAR estimates. The model presented has several common features with \cite{greenwood1997long} that design a two-sector economy where one sector displays a faster technology than the other. One different is that we focus specifically on ICT capital sector, rather than equipment, as the sector with faster technological improvements. This assumption will be necessary if we want to fit the fact that relative prices between the ICT investment and overall economy display a downward sloping trend.\footnote{In addition, we also rely on the results of \cite{whelan2003two} and \cite{oulton2007investment} to correctly define productivity and output share in our setting.}

>>>>

In the previous section, we have documented results regarding the relation of current ICT investment and future productivity. Clearly, to rationalize the empirical responses of aggregate macroeconomic variables to ICT shocks, we need a two-sector approach that distinguishes ICT goods from other output. In this section, we present a simple two-sector model that rationalizes our structural VAR estimates.

% Need to add something here that says that we investigate whether a spillover can explain things.

The model presented has several common features with the two-sector environment of \cite{greenwood1997long} that design a two-sector economy where one sector displays a faster technology than the other. One different is that we focus specifically on ICT capital sector, rather than equipment, as the sector with faster technological improvements. This assumption will be necessary if we want to fit the fact that relative prices between the ICT investment and overall economy display a downward sloping trend.\footnote{In addition, we also rely on the results of \cite{whelan2003two} and \cite{oulton2007investment} to correctly define productivity and output share in our setting.}
